Coalescent inference of mutation spectrum histories from sample frequency spectra

### 2019-09-09 manuscript/main.tex

Single nucleotide variant (SNV) frequencies partitioned according to triplet nucleotide context vary among human ancestry groups and among great ape species, indicating variation and divergence of the mutation process.
The sample frequency spectrum (SFS)---the distribution of derived allele frequencies among sampled haplotypes---is a well-studied population genetic summary statistic that is sensitive to demographic history.
We extend a coalescent framework for demographic inference from the SFS to accommodate inference of mutation spectrum histories from the triplet-resolved sample frequency spectrum (3-SFS).
We formulate inference of mutation spectrum histories from the 3-SFS as a linear inverse problem.

>>>>

Single nucleotide variant (SNV) frequencies partitioned according to triplet nucleotide context vary among human ancestry groups and among great ape species, indicating variation and divergence of the mutation process.
The sample frequency spectrum (SFS)---the distribution of derived allele frequencies among sampled haplotypes---is a well-studied population genetic summary statistic that is sensitive to demographic history.
We extend a coalescent framework for demographic inference from the SFS to accommodate inference of mutation spectrum histories from the sample frequency spectrum resolved by $k$-mer nucleotide context ($k$-SFS).
We formulate inference of mutation spectrum histories from the $k$-SFS as a linear inverse problem.
